\documentclass[11pt,letterpaper,sans,unicode]{moderncv}
\usepackage{babel,xpatch}
\usepackage{graphicx}
\usepackage{longtable}
\usepackage{multirow}
%\usepackage{enumitem}
\usepackage{relsize}
\usepackage{textcomp}
\usepackage{units}
\usepackage{lineno}
\usepackage{rotating}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage[utf8]{inputenc}
\usepackage{longtable}
\usepackage{xcolor}
\usepackage[gen]{eurosym}
\usepackage{comment}
\usepackage{etaremune}

%\usepackage[T1]{fontenc}
%\usepackage{hyperref}
%\usepackage[latin9]{inputenc}


\moderncvstyle{banking}
\moderncvcolor{blue}

\renewcommand{\familydefault}{\sfdefault}
\usepackage[top=0.7in,bottom=0.7in,left=1in,right=1in,bindingoffset=0cm]{geometry}
\setlength{\hintscolumnwidth}{3cm}
\usepackage{enumitem}
\setlist{nolistsep}
\usepackage{lastpage}
\usepackage{mathabx}
\cfoot{{\color{gray} Page \thepage\ of \pageref{LastPage}}}

\def\baas{{Bulletin of AAS}}               % Bulletin of the AAS
\def\prd{{Phys. Rev.} D}
\def\prl{{Phys.Rev.} Lett}
\def\ajp{{Amer. J. Phys}}
\def\apjl{{Astrophys. J.} Lett}
\def\apj{{Astrophys. J.}}
\def\cqg{{Class. Quantum Grav.}}
\def\aaps{{A\&AS}}
\def\pasj{{PASJ}}
\def\mnras{{MNRAS}}
\def\aapr{{A\&ARv}}
\def\aap{{A\&A}}
\def\grg{{Gen. Rel.\&Grav.}}
\def\na{{New Astronomy}}
\def\ptp{{Progress of Theoretical Physics}}
\def\apjs{{ApJS}}
\def\araa{{ARA\&A}}
\def\ssr{{Space Sci. Rev.}}
\def\jpcs{{J. Phys. Conf. Ser.}}
\def\npb{{Nucl. Phys. B}}
\def\clrpaawp{{Can. Lon. Ran. Plan A\&A}}


\newcommand{\cvreference}[9]{%
  \textbf{#1}\newline% Name
  \ifthenelse{\equal{#2}{}}{}{\addresssymbol~#2\newline}%
  \ifthenelse{\equal{#3}{}}{}{#3\newline}%
  \ifthenelse{\equal{#4}{}}{}{#4\newline}%
  \ifthenelse{\equal{#5}{}}{}{#5\newline}%
  \ifthenelse{\equal{#6}{}}{}{#6\newline}%
  \ifthenelse{\equal{#7}{}}{}{#7\newline}%
  \ifthenelse{\equal{#8}{}}{}{\emailsymbol~{\footnotesize \texttt{\emaillink[]{#8}}}\newline}
  \ifthenelse{\equal{#9}{}}{}{\phonesymbol~#9}
  }


%%%%%% My Macros %%%%%
\newcommand{\pubitem}[4]{\item \cvitem{}{\textit{#1}.\\ {#2} \\{\color{color1} \href{#3}{\color{color1} #4}} }\vspace{-0.3cm}} %title, authors, href, journal %\textcolor{red}{$\bullet$} $141$ citations.

\newcommand{\software}[3]{\cventry{}{\bbullet #2}{\hspace{2mm}\texttt{#1}}{}{}{\bbullet \color{color1} \url{#3}}} %Name, Description, URL
%\vspace{-0.1cm}

\newcommand{\blucirc}{{\color{color1} $\circ\;\;$}}
\newcommand{\bbullet}{\hspace{0.4cm}\blucirc}

%----------------------------------------------------------------------------------------
%   NAME AND CONTACT INFORMATION SECTION
%----------------------------------------------------------------------------------------

\firstname{\huge{Jeffrey~S.}} % Your first name
\familyname{\huge{Hazboun}} % Your last name

% All information in this block is optional, comment out any lines you don't need
\title{\huge{Publications}}
\address{Physical Sciences Division, University of Washington Bothell}{18115 Campus Way NE Bothell, WA 98011-8246, USA}
\phone[mobile]{+1~(801)~440~2156}
\email{hazboun@uw.edu}
\homepage{jeffreyhazboun.github.io}
\social[github]{Hazboun6}
\social[twitter]{jeffreyhazboun}
%\social[linkedin][linkedin.com/in/]{stephen-taylor}

\lhead{{\color{gray} \fontsize{10}{22}\mdseries\upshape{Jeffrey~S.~Hazboun}}}
\rhead{{\color{gray} \fontsize{10}{10}\mdseries\upshape{hazboun@uw.edu}}}

%\definecolor{color1}{HTML}{1f77b4}
%\hypersetup{urlcolor=color1,linkcolor=color1}

\begin{document}
\makecvtitle

\vspace{-13mm}
%----------------------------------------------------------------------------------------
%  FULL PUBLICATION LIST
%----------------------------------------------------------------------------------------

\section{Publications}

$\bullet$ \textbf{Metrics} available at {\color{color1} \href{https://scholar.google.com/citations?user=CbNY_MYAAAAJ&hl=en}{Google Scholar}}.

\subsection{Submitted}

\begin{etaremune}[leftmargin=8mm]
\input{sub_entries}
\end{etaremune}

\subsection{Published}

\begin{etaremune}[leftmargin=8mm]
\input{pub_entries}
\end{etaremune}

\subsection{Technical and White Papers}

\begin{etaremune}[leftmargin=8mm]
\input{wp_entries}
\end{etaremune}

\section{Software Development}
\subsection{Lead Developer}
\software{Hasasia}{Python package for calculating pulsar timing array sensitivity curves and signal-to-noise ratios.}{https://pypi.org/project/hasasia/}
\software{Pulsar Signal Simulator}{Python package for simulating pulsar observation data.}{https://github.com/PsrSigSim/PsrSigSim}
\software{La Forge}{Python package for processing data from Bayesian analyses of PTA data.}{https://pypi.org/project/la-forge/}
\software{Pulsar Data Toolbox}{Python package for accessing pulsar data files.}{https://pypi.org/project/pdat/}

\subsection{Development Team}
\software{Enterprise}{Python package for bayesian PTA data analysis.}{https://github.com/nanograv/enterprise}
\software{enterprise\underline{ }extensions}{Python package for building bayesian analysis models.}
{https://github.com/nanograv/enterprise_extensions}
\software{gwent}{Python package calculating gravitational wave sensitivities across the spectrum}{https://pypi.org/project/gwent/}
\software{Tabletop PTA}{Python package for an acoustical PTA demonstration.}{https://pypi.org/project/tabletop_pta/}

\end{document}
