\documentclass[11pt,letterpaper,sans,unicode]{moderncv}
\usepackage{xpatch}
\usepackage{graphicx}
\usepackage{longtable}
\usepackage{multirow}
%\usepackage{enumitem}
\usepackage{relsize}
\usepackage{textcomp}
\usepackage{units}
\usepackage{lineno}
\usepackage{rotating}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage[utf8]{inputenc}
\usepackage{longtable}
\usepackage{xcolor}
\usepackage[gen]{eurosym}
\usepackage{comment}
\usepackage{etaremune}

%\usepackage[T1]{fontenc}
%\usepackage{hyperref}
%\usepackage[latin9]{inputenc}


\moderncvstyle{banking}
\moderncvcolor{blue}

\renewcommand{\familydefault}{\sfdefault}
\usepackage[top=0.7in,bottom=0.7in,left=1in,right=1in,bindingoffset=0cm]{geometry}
\setlength{\hintscolumnwidth}{3cm}
\usepackage{enumitem}
\setlist{nolistsep}
\usepackage{lastpage}
\usepackage{mathabx}
\cfoot{{\color{gray} Page \thepage\ of \pageref{LastPage}}}

\def\baas{{Bulletin of AAS}}               % Bulletin of the AAS
\def\prd{{Phys. Rev.} D}
\def\prl{{Phys.Rev.} Lett}
\def\ajp{{Amer. J. Phys}}
\def\apjl{{Astrophys. J.} Lett}
\def\apjs{{Astrophys. J.} Supp}
\def\apj{{Astrophys. J.}}
\def\cqg{{Class. Quantum Grav.}}
\def\aaps{{A\&AS}}
\def\pasj{{PASJ}}
\def\mnras{{MNRAS}}
\def\aapr{{A\&ARv}}
\def\aap{{A\&A}}
\def\grg{{Gen. Rel.\&Grav.}}
\def\na{{New Astronomy}}
\def\ptp{{Progress of Theoretical Physics}}
\def\araa{{ARA\&A}}
\def\ssr{{Space Sci. Rev.}}
\def\jpcs{{J. Phys. Conf. Ser.}}
\def\npb{{Nucl. Phys. B}}
\def\clrpaawp{{Can. Lon. Ran. Plan A\&A}}


\newcommand{\cvreference}[9]{%
  \textbf{#1}\newline% Name
  \ifthenelse{\equal{#2}{}}{}{\addresssymbol~#2\newline}%
  \ifthenelse{\equal{#3}{}}{}{#3\newline}%
  \ifthenelse{\equal{#4}{}}{}{#4\newline}%
  \ifthenelse{\equal{#5}{}}{}{#5\newline}%
  \ifthenelse{\equal{#6}{}}{}{#6\newline}%
  \ifthenelse{\equal{#7}{}}{}{#7\newline}%
  \ifthenelse{\equal{#8}{}}{}{\emailsymbol~{\footnotesize \texttt{\emaillink[]{#8}}}\newline}
  \ifthenelse{\equal{#9}{}}{}{\phonesymbol~#9}
  }


%%%%%% My Macros %%%%%
\newcommand{\editem}[7]{\cventry{#1}{\hspace{4mm}#2 \vspace*{1mm}}{#3}{#4}{}{\hspace{4mm}\textbf{Advisor:} #5}{\hspace{4mm}\textbf{#6:} \textit{#7} }}
%School City/State, School, Degree, Degree Date, Advisor, title type, title

\newcommand{\bsitem}[4]{\cventry{#1}{\hspace{4mm}#2 \vspace*{1mm}}{#3}{#4}{}{}{}}
%School City/State, School, Degree, Degree Date

\newcommand{\pubitem}[4]{\item \cvitem{}{\textit{#1}.\\ {#2} \\{\color{color1} \href{#3}{\color{color1} #4}} }\vspace{-0.3cm}} %title, authors, href, journal %\textcolor{red}{$\bullet$} $141$ citations.

\newcommand{\software}[3]{\cventry{}{\bbullet #2}{\hspace{2mm}\texttt{#1}}{}{}{\bbullet \color{color1} \url{#3}}} %Name, Description, URL
%\vspace{-0.1cm}

\newcommand{\talkitem}[3]{\item \textit{#1}\\{#2}, #3} %Title, Meeting, Date
\newcommand{\invtalkitem}[3]{\item \textbf{#1}, \hfill{#2} \\ \textit{\color{color1}``#3''} \vspace{-0.1cm}} %Place, Title, Date

%\newcommand{\invtalkitem}[3]{\cvitemwithcomment{}{\item #1 \color{color1}\textit{``#2''}}{#3} \vspace{-0.1cm}}
\newcommand{\outtalkitem}[4]{\cvitemwithcomment{}{\bbullet #1, #2 \color{color1}\textit{``#3''}}{#4} \vspace{-0.1cm}} %What, Where, Title, Year
\newcommand{\studentitem}[4]{\item \textit{#1}, {#2} \hfill{#3} \\ \textit{``#4''} } %Name, School, Date, Title\vspace{-0.1cm}
\newcommand{\confitem}[2]{\item #1 \hfill #2} %Meeting, Date

\newcommand{\blucirc}{{\color{color1} $\circ\;\;$}}
\newcommand{\bbullet}{\hspace{0.4cm}\blucirc}

%----------------------------------------------------------------------------------------
%   NAME AND CONTACT INFORMATION SECTION
%----------------------------------------------------------------------------------------

\firstname{\huge{Jeffrey~S.}} % Your first name
\familyname{\huge{Hazboun}} % Your last name

% All information in this block is optional, comment out any lines you don't need
\title{\huge{Curriculum Vitae}}
\address{Department of Physics, Oregon State University}{313 Weniger Hall Corvallis, OR 97331-6507, USA}
%\phone[mobile]{+1~(801)~440~2156}
\phone{+1~(541)~737~1242}
\email{hazboun@uw.edu}
\homepage{jeffreyhazboun.github.io}
\social[github]{Hazboun6}
\social[twitter]{jeffreyhazboun}
%\social[linkedin][linkedin.com/in/]{stephen-taylor}

\lhead{{\color{gray} \fontsize{10}{22}\mdseries\upshape{Jeffrey~S.~Hazboun}}}
\rhead{{\color{gray} \fontsize{10}{10}\mdseries\upshape{hazboun@uw.edu}}}

%\definecolor{color1}{HTML}{1f77b4}
%\hypersetup{urlcolor=color1,linkcolor=color1}

\begin{document}
\makecvtitle

\vspace{-13mm}
%----------------------------------------------------------------------------------------
%   WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{Professional Experience}

\cventry{September 2022--Present}{\hspace{0.4cm}{\blucirc}Assistant Professor of Physics}
{\textsc{Oregon State University}}
{Corvallis, OR}{}{} %\vspace{-6mm}
%

\cventry{August 2018--September 2022}{\hspace{0.4cm}{\blucirc}NANOGrav Physics Frontiers Center Senior Postdoctoral Fellow}
{\textsc{University of Washington Bothell}}
{Bothell, WA}{}{} %\vspace{-6mm}
%
\cventry{August 2016--July 2018}{\hspace{0.4cm}{\blucirc}NANOGrav Physics Frontiers Center Postdoctoral Fellow}{\textsc{University of Texas Rio Grande Valley}}{Brownsville, TX}{}{} %\vspace{-6mm}
%
\cventry{August 2015--July 2016}{\hspace{0.4cm}{\blucirc}Visiting Assistant Professor}{\textsc{Hendrix College}}{Conway, AR}{}{}
%
\cventry{September 2014 - August 2015}{\hspace{0.4cm}{\blucirc}Postdoctoral Teaching Position/ Head Online Class Developer}
{\textsc{Utah State University}}{Logan, UT}{}{}
%
\cventry{June 2012 - May 2013}{\hspace{0.4cm}{\blucirc}Visiting Scholar, Center for Relativistic Astrophysics}
{\textsc{Georgia Institute of Technology}}{Atlanta, GA}{}{}
%----------------------------------------------------------------------------------------
%   EDUCATION SECTION
%----------------------------------------------------------------------------------------
%\vspace{-3mm}
\section{Education}
%School City/State, School, Degree, Degree Date, Advisor, title type, title

\editem{Logan, Utah}{Utah State University}{PhD in Physics}{December 2014}{Dr.~James~T.~Wheeler}{Dissertation Title}{Conformal gravity and time}
\vspace{2mm}

\editem{Corvallis, Oregon}{Oregon State University}{MS Physics  (Mathematics Minor)}{June 2008}{Dr.~Tevian~Dray}{Thesis Title}{The effects of negative-energy shells on Schwarzschild spacetime}
\vspace{2mm}

\bsitem{Syracuse, New York}{State University of New York, College of Environmental Science and Forestry}{BS Biology}{December 1999}

%----------------------------------------------------------------------------------------
%   RESEARCH SECTION
%----------------------------------------------------------------------------------------
%\vspace{-4mm}
%\section{Research Interests}
%\cvitem{Primary interests}{gravitational-wave astronomy~$\bullet$~theoretical astrophysics~$\bullet$~massive black-hole binaries~$\bullet$~stellar-mass compact objects~$\bullet$~pulsar timing~$\bullet$~statistical inference}
%\cvitem{Secondary interests}{galaxy formation and evolution~$\bullet$~cosmology~$\bullet$~pulsar physics and demographics~$\bullet$~ionized interstellar medium}
%\cvitem{Specific interests}{Bayesian hierarchical modeling~$\bullet$~pulsar-timing data-analysis for nanohertz gravitational-wave searches~$\bullet$~compact-binary demographics and population inference~$\bullet$~pulsar-timing noise characterization and mitigation~$\bullet$~waveform modeling for supermassive black-hole binary searches~$\bullet$~modeling final-parsec dynamics of supermassive black-hole binaries~$\bullet$~stochastic signal analysis strategies}

%----------------------------------------------------------------------------------------
%   GRANTS & FUNDING
%----------------------------------------------------------------------------------------

\section{Grants, Funding \& Awards}

\cvitemwithcomment{}{\textbf{Proposal (PI): ``Pulsar Timing Array GW Signal Analysis Using Big Data Techniques''}}{2019}
\begin{tabular}{rcl}
&\hspace{0.4cm} &{\color{color1} $\circ\;\;$}PI Jeffrey Hazboun, a submission to Amazon Web Services Machine Learning Research Awards. \\
&\hspace{0.4cm} &  {\color{color1} $\circ\;\;$}Total award: $\$50,000$ in AWS Promotional Credits.\\
\end{tabular} \\

%----------------------------------------------------------------------------------------
%  OBSERVING PROPOSALS
%----------------------------------------------------------------------------------------
%\vspace{-4mm}
\section{Observing Proposals}
{\small
\cvitemwithcomment{}{Co-I: \textbf{``Monitoring pulse-shape changes in the IPTA pulsar sample"}}{May 2021}
\begin{tabular}{rcl}
&\hspace{0.4cm} &{\color{color1} $\circ\;\;$}Giant Metrewave Radio Telescope, Target of Opportunity proposal  \\
&\hspace{0.4cm} &{\color{color1} $\circ\;\;$}Status: awarded $10.0$ hours
\end{tabular} \\

\cvitemwithcomment{}{Co-I: \textbf{``Tracking Rapid and Unexpected Pulse Shape Changes in the MSP~J1713+0747"}}{May 2021}
\begin{tabular}{rcl}
&\hspace{0.4cm} &{\color{color1} $\circ\;\;$}Very Large Array, Director's discretionary time proposal VLA/$21A-426$ \\
&\hspace{0.4cm} &{\color{color1} $\circ\;\;$}Status: awarded $14.0$ hours
\end{tabular} \\

\cvitemwithcomment{}{Co-I: \textbf{``Monitoring pulse shape changes in the International Pulsar Timing Array"}}{June 2021}
\begin{tabular}{rcl}
&\hspace{0.4cm} &{\color{color1} $\circ\;\;$}Parkes Observatory, Non A-priori Assignable Proposal \\
&\hspace{0.4cm} &{\color{color1} $\circ\;\;$}Status: awarded $10.0$ hours
\end{tabular} \\

\cvitemwithcomment{}{Co-I: \textbf{``High Cadence Observations of MSPs for Gravitational Wave Detection"}}{March 2020}
\begin{tabular}{rcl}
&\hspace{0.4cm} &{\color{color1} $\circ\;\;$}Arecibo Radio Telescope, proposal P$2945$ \\
&\hspace{0.4cm} &{\color{color1} $\circ\;\;$}Status: awarded $32.5$ hours
\end{tabular} \\

\cvitemwithcomment{}{Co-I: \textbf{``High Time Resolution Observations of a Bright Millisecond Pulsar"}}{November 2018}
\begin{tabular}{rcl}
&\hspace{0.4cm} &{\color{color1} $\circ\;\;$}Greenbank Telescope, Project ID GBT$18B-355$ \\
&\hspace{0.4cm} &{\color{color1} $\circ\;\;$}Status: awarded $5$ hours
\end{tabular}
}

%\vspace{-10mm}
%----------------------------------------------------------------------------------------
%  FULL PUBLICATION LIST
%----------------------------------------------------------------------------------------

\section{Publications}

%\cvitem{}
%{
%\begin{tabular}{rcl}
%\textbf{Counts}: &\hspace{0.3cm} &{\textbf{44} papers published in major peer-reviewed journals} \\
%& &{(out of which \textbf{12} are first-authored papers, and \textbf{4} papers were covered by press releases).}
%\end{tabular}
%}

%$\bullet$ \textbf{Total number of citations:} 2650 (using Google Scholar), \textbf{h-index:} 27, \textbf{i10-index:} 34

$\bullet$ \textbf{Metrics} available at {\color{color1} \href{https://inspirehep.net/literature?sort=mostrecent&size=25&page=1&q=a%20J.S.Hazboun.1&ui-citation-summary=true}{InspireHEP} or \href{https://scholar.google.com/citations?user=CbNY_MYAAAAJ&hl=en}{Google Scholar}}.

\subsection{Submitted}

%\begin{etaremune}[leftmargin=8mm]
%\input{sub_entries}
%\end{etaremune}

\subsection{Accepted}

\begin{etaremune}[leftmargin=8mm]
\input{accept_entries}
\end{etaremune}

\subsection{Published}

\begin{etaremune}[leftmargin=8mm]
\input{pub_entries}
\end{etaremune}

\subsection{Technical and White Papers}

\begin{etaremune}[leftmargin=8mm]
\input{wp_entries}
\end{etaremune}

%----------------------------------------------------------------------------------------
%   TEACHING SECTION
%----------------------------------------------------------------------------------------
%\vspace{-4mm}
\section{Teaching \& Mentoring}

%\textbf{\textcolor{black}{Lecturing:}}
\subsection{Teaching Positions}
	\renewcommand\labelitemi{\blucirc}
	\begin{itemize}[leftmargin=8mm]
	\setlength\itemsep{1mm}
	\item \textbf{\color{color1} Visiting Assistant Professor}, Hendrix College, \hfill Fall 2015 - Spring 2016
        		\newline  \textit{Astronomy, Cosmology, Quantum Mechanics, and General Physics I}
		\newline Mentored 4 undergraduate researchers.
        \item \textbf{\color{color1} Physics Instructor}, Utah State University, \hfill Spring 2015
        		\newline \textit{General Physics II:} Physics for the Life Sciences class.
		\newline Instructor of Record for 165 students.
		\newline Supervised nine teaching assistants.
        \item \textbf{\color{color1} Astronomy Instructor}, Utah State University, \hfill Fall 2014
        		\newline Instructor of record for a 300+ person astronomy class.
		\newline Supervised two teaching assistants.
        \item \textbf{\color{color1} Online Physics Course Developer \& Instructor}, Utah State University, \hfill 2012-2014
        		\newline \textit{The Universe:} Proposed, developed and taught an online cosmology class.
		\newline Aimed at non-science majors.
		\newline Continuously offered for the last 7 semesters.
		\newline Over 2000 students have taken this class.
        \item \textbf{\color{color1} Physics Instructor}, Utah State University, \hfill Summer 2011
        		\newline \textbf\emph{General Physics I:} Instructor of Record
	\item \textbf{\color{color1} MCAT Physics Instructor} Princeton Review, Portland, Oregon, \hfill Summer 2007
		\newline Developed curriculum to help students review for physics portion of the MCAT exam.
		\newline Taught students test-taking strategies to prepare for a stressful and fast-paced exam.
	\end{itemize}

\subsection{Courses}
	\hspace{8mm}\textbf{\color{color1} Courses Instructed,} \emph{Textbook}  (Students $\times$ Credit Hours $\!$) {\footnotesize [cumulative]}

	\vspace*{1mm}

	\begin{itemize}[leftmargin=8mm]
        		\item \textbf{\color{color1} Quantum Mechanics,} \emph{Griffiths} (39 hrs)
			\item \textbf{\color{color1} Cosmology,} \emph{Ryden} (27 hrs)
			\item \textbf{\color{color1} Astronomy,} \emph{Bennett, et al.} (1300 hrs)
			\item \textbf{\color{color1} The Universe,} \emph{Ratcliffe} (1200 hrs)
			\item \textbf{\color{color1} Physics for the Life Sciences 1,} \emph{Cutnell \& Johnson} (75 hrs)
			\item \textbf{\color{color1} Physics for the Life Sciences 2,} \emph{Cutnell \& Johnson} (450 hrs)
			\item \textbf{\color{color1} Physics for Engineers 1,} \emph{Halliday \& Resnick} (75 hrs)
        \end{itemize}


%\subsection{Postdoctoral scholar mentoring}

%\cvitemwithcomment{}{\hspace{0.4cm}${\color{color1} \circ}\;$ \textit{Dr.~Maria~Charisi}, Vanderbilt University}{Oct 2020--}\vspace{-0.1cm}
%\hspace{0.71cm} Vanderbilt Initiative in Data-intensive Astrophysics (VIDA) Fellow %\vspace{-0.1cm}

%\cvitemwithcomment{}{\hspace{0.4cm}${\color{color1} \circ}\;$ \textit{Dr.~Nihan~Pol}, Vanderbilt University}{Sep 2020--}\vspace{-0.1cm}
%\hspace{0.71cm} Vanderbilt Initiative in Data-intensive Astrophysics (VIDA) Fellow %\vspace{-0.1cm}

\subsection{Graduate Student Research Mentoring}
\renewcommand\labelitemi{\blucirc}
\begin{itemize}[leftmargin=8mm]
	\studentitem{Brent Shapiro-Albert}{West Virginia University}{2018-2020}{Chromatic Covariances with the Pulsar Signal Simulator}
	\studentitem{Andrew Kaiser}{West Virginia University}{2018-2020}{Bayesian Non-Linear Timing with Gravitational Wave PTA Software}

\end{itemize}


\subsection{Undergraduate Student Research Mentoring}
\renewcommand\labelitemi{\blucirc}
\begin{itemize}[leftmargin=8mm]
	\studentitem{Christine Ye}{University of Washington Bothell}{2020-}{PTA False Alarm Studies}
	\studentitem{Min Young Kim}{University of Washington Seattle}{2018-2019}{Bayesian Pulsar Timing}
	\studentitem{Kyle Gersbach}{University of Washington Bothell}{2018-2020}{Teaching with the Pulsar Signal Simulator}
	\studentitem{Jacob Hesse}{University of Washington Bothell}{2017-2018}{Efficiently Simulating NANOGrav Pulsars}
	\studentitem{Amelia Henkel}{REU UT Rio Grande Valley}{Summer 2017}{Dispersing Simulated Baseband Pulsar Signals}
	\studentitem{Cassidy Wagner}{REU UT Rio Grande Valley}{Summer 2017}{Simulating Interstellar Medium Effects with Convolution}
       	 \studentitem{Chris Griffin}{Hendrix College}{2015-2016}{Conformal Diagrams of Crossing Spherical Shells in Schwarzschild Spacetime}
      	\studentitem{Devon Roell}{Hendrix College}{2015-2016}{The Quantum Exchange Force and Gravity}
	\studentitem{Eric Mullins}{Hendrix College}{2015-2016}{Localizing Gravitational Wave Sources with Noisy Null Signals}
	\studentitem{Connor Nelson}{Hendrix College}{2015-2016}{Localizing Multiple Gravitational Wave Sources with Null Signals}
        	\studentitem{Manuel Pichardo Marcano}{Utah State University}{2012-2013}{Multi-messenger Pulsar Timing Array Sources and Propagation Tests}
\end{itemize}

%\textbf{\textcolor{black}{Teaching assistant:}}
\subsection{Teaching assistant}

\begin{itemize}[leftmargin=8mm]
	\item Utah State University \hfill Fall 2009-Spring 2012
            	\newline \textit{General Physics I:} Recitation Leader and Lab Instructor
            	\newline \textit{General Physics II:} Recitation Leader and Lab Instructor
       	 \item Oregon State University  \hfill Fall 2006-Spring 2009
            	\newline \textit{Paradigms in Physics TA:} NSF funded higher division class reform project.
		\newline Facilitated group work and took part in curriculum meetings.
           	\newline \textit{Physics for the Life Sciences:} Recitation Leader and Lab Instructor
            	\newline \textit{General Physics II:} Lab Instructor
\end{itemize}

%----------------------------------------------------------------------------------------
%   OUTREACH SECTION
%----------------------------------------------------------------------------------------
%\vspace{-2mm}
\section{Leadership \& Professional Service}

\subsection{Research leadership}

\cvitemwithcomment{}{\hspace{0.15cm}${\color{color1} \circ}\;$ \textit{\textbf{Co-chair}}, IPTA Gravitational Wave Analysis Group}{Jan 2019--} \vspace{-0.1cm}

\cvitemwithcomment{}{\hspace{0.15cm}${\color{color1} \circ}\;$ \textit{\textbf{Co-chair}}, IGRAV Diversity, Equity \& Inclusion Working Group}{Jan 2019--July 2021} \vspace{-0.1cm}

\cvitemwithcomment{}{\hspace{0.15cm}${\color{color1} \circ}\;$ \textit{\textbf{Co-chair}}, IPTA Data Challenge Group}{Mar 2018--} \vspace{-0.1cm}

\subsection{Reviewer for international journals}
\hspace{0.5mm} \blucirc The Astrophysical Journal  \hfill \blucirc Classical and Quantum Gravity \hfill \hspace{-0.2cm} \blucirc Physical Review D

\hspace{0.5mm} \blucirc General Relativity \& Gravitation  \hfill \blucirc Monthly Notices of the Royal Astronomical Society

\hspace{0.5mm} \blucirc Physical Review Letters  \hfill \blucirc European Journal of Physics

%\vspace{-5mm}

\subsection{Conference organization}
	\begin{itemize}[leftmargin=8mm]
	\confitem{Local Organizing Committee, Conferences for Undergraduate Women in Physics, UW Seattle}{2019}
	\confitem{Local Organizing Committee Chair, NANOGrav Spring Meeting, UW Bothell}{2019}
	\confitem{LISA Data Analysis Workshop, AAS233}{2019}
	\confitem{Scientific Organizing Committee, LISA Symposium, Chicago}{2018}
	\confitem{Scientific Organizing Committee, NANOGrav Spring Meeting, University of Virginia}{2018}
	\confitem{Scientific Organizing Committee, NANOGrav Spring Student Workshop, University of Virginia}{2018}
    	\confitem{Student Workshop Organizer, IPTA Meeting, Paris, France}{2017}
	\confitem{Session Chair, \emph{Black Holes}, AAS235}{2020}
	\confitem{Session Chair, LISA Symposium}{2018}
	\end{itemize}

%\subsection{Seminar organization}
%\cvitemwithcomment{}{\hspace{0.4cm}${\color{color1} \circ}\;$ Caltech TAPIR Seminar Series \textit{(executive committee)}}{2019} \vspace{-0.1cm}
%\cvitemwithcomment{}{\hspace{0.4cm}${\color{color1} \circ}\;$ Caltech/JPL Association for Gravitational-Wave Research \textit{(executive committee)}}{2017--2019} \vspace{-0.1cm}
%\cvitemwithcomment{}{\hspace{0.4cm}${\color{color1} \circ}\;$ Caltech TAPIR and LIGO postdoctoral lunch seminar series}{2015--2016} \vspace{-0.1cm}
\begin{comment}
\subsection{Committees}
\cvitemwithcomment{}{\hspace{2mm}${\color{color1} \circ}\;$ NANOGrav chapter of the {\color{color1} \href{https://www.aps.org/programs/innovation/fund/idea.cfm}{APS Inclusion, Diversity, \& Equity Alliance}}}{Jul 2020--} \vspace{-0.1cm}
\end{comment}

\subsection{Code \& data sharing}

\cvitemwithcomment{}{\hspace{2mm}${\color{color1} \circ}\;$ Jupyter Notebook examples for \texttt{pta\_forecasts}. Based on \url{arxiv.org/abs/2009.11865}}{2020} \vspace{-0.1cm}
\hspace{0.71cm} {\color{color1} \url{https://github.com/Hazboun6/pta_forecasts}}

\cvitemwithcomment{}{\hspace{2mm}${\color{color1} \circ}\;$ Introductory data analysis tutorial.}{2019} \vspace{-0.1cm}
\hspace{0.71cm} {\color{color1} \url{https://github.com/Hazboun6/data_analysis_tutorial}}

\cvitemwithcomment{}{\hspace{2mm}${\color{color1} \circ}\;$ Developer of open-source Python GW analysis software \texttt{enterprise}}{2017--} \vspace{-0.1cm}
\hspace{0.71cm} {\color{color1} \url{https://github.com/nanograv/enterprise}}


\subsection{Professional affiliations}
%
\cvitemwithcomment{}{\hspace{0.4cm}${\color{color1} \circ}\;$ LISA Consortium, \textit{Member}}{} \vspace{-0.1cm}

\cvitemwithcomment{}{\hspace{0.4cm}${\color{color1} \circ}\;$ North American Nanohertz Observatory for Gravitational-waves (NANOGrav), \textit{Full member}}{} \vspace{-0.1cm}
\cvitemwithcomment{}{\hspace{0.4cm}${\color{color1} \circ}\;$ International Pulsar Timing Array (IPTA), \textit{Member}}{} \vspace{-0.1cm}
\cvitemwithcomment{}{\hspace{0.4cm}${\color{color1} \circ}\;$ American Physical Society (DGRAV), \textit{Member}}{} \vspace{-0.1cm}
%\vspace{-0.1cm}
\cvitemwithcomment{}{\hspace{0.4cm}${\color{color1} \circ}\;$ American Astronomical Society, \textit{Member}}{} \vspace{-0.1cm}

\section{Software Development}
\subsection{Lead Developer}
\software{Hasasia}{Python package for calculating pulsar timing array sensitivity curves and signal-to-noise ratios.}{https://pypi.org/project/hasasia/}
\software{Pulsar Signal Simulator}{Python package for simulating pulsar observation data.}{https://github.com/PsrSigSim/PsrSigSim}
\software{La Forge}{Python package for processing data from Bayesian analyses of PTA data.}{https://pypi.org/project/la-forge/}
\software{Pulsar Data Toolbox}{Python package for accessing pulsar data files.}{https://pypi.org/project/pdat/}

\subsection{Development Team}
\software{Enterprise}{Python package for bayesian PTA data analysis.}{https://github.com/nanograv/enterprise}
\software{enterprise\underline{ }extensions}{Python package for building bayesian analysis models.}
{https://github.com/nanograv/enterprise_extensions}
\software{gwent}{Python package calculating gravitational wave sensitivities across the spectrum}{https://pypi.org/project/gwent/}
\software{Tabletop PTA}{Python package for an acoustical PTA demonstration.}{https://pypi.org/project/tabletop_pta/}
%\vspace{-0.1cm}

%\vspace{-3mm}
\section{Outreach, Diversity, \& Media Engagement}

\subsection{Outreach}
\renewcommand\labelenumi{\bfseries\theenumi .}
\small
\outtalkitem{North City Tech Meetup}{}{Searching for Gravitational Waves with a Galactic-Scale Detector}{2021}
\outtalkitem{Gravitational Wave Astronomy}{Eastside Preparatory}{How are gravitational waves detected?}{2020}
\outtalkitem{Science Wednesday Panel Discussion}{King's Live Music}{The Science of Time Travel}{2015}
\outtalkitem{Science Fiction Club Talk}{Hendrix College}{Black Holes and Wormholes}{2015}
\outtalkitem{Science Unwrapped (500 person public lecture)}{Utah State University}{Explore to Conserve}{2013}
\outtalkitem{Conservation Club Talk}{Weber State}{A Scientist's Role in Conservation}{2012}
\outtalkitem{Science Unwrapped}{Swaner Ecocenter}{A Scientist's Role in Modern Exploration}{2012}
\outtalkitem{Cache Valley Stargazers Talk}{Logan, UT}{Black Holes: Ninjas of the Night Sky}{2009}

\subsection{Diversity \& Equity}
\begin{itemize}[leftmargin=8mm]
\item Founding Co-chair, Diversity Equity \& Inclusion Working Group,  {\color{color1} \href{https://indico.ego-gw.it/event/29/sessions/53/attachments/420/685/International_Gravitational-Wave_Outreach_Group_Meeting__Briefing_Document.pdf}{International Gravitational Outreach Group}}
\item Member of the NANOGrav chapter of the {\color{color1} \href{https://www.aps.org/programs/innovation/fund/idea.cfm}{APS Inclusion, Diversity, \& Equity Alliance}}
\item Local Organizing Committee, UW, Seattle (2019) {\color{color1} \href{https://www.aps.org/programs/women/cuwip/cuwiphistory.cfm}{Conferences for Undergraduate Women in Physics}}
%\item As an LOC member for the Spring 2018 NANOGrav collaboration meeting at UW Bothell, I coordinated with the Bothell Center for Diversity on a seminar to promote allyship, inclusiveness, and equity within the NANOGrav collaboration.
\end{itemize}

\begin{comment}
\subsection{Press releases}

\cvitemwithcomment{}{\hspace{0.4cm}${\color{color1} \circ}\;$ {\color{color1} \href{https://news.vanderbilt.edu/2020/06/30/to-find-giant-black-holes-start-with-jupiter/}{``\textit{To find giant black holes, start with Jupiter}''}}}{Jun 2020} \vspace{-0.1cm}
\hspace{0.71cm} Collaboration research (Vanderbilt press release)  \\
\cvitemwithcomment{}{\hspace{0.4cm}${\color{color1} \circ}\;$ {\color{color1} \href{https://greenbankobservatory.org/to-find-giant-black-holes-start-with-jupiter/}{``\textit{To find giant black holes, start with Jupiter}''}}}{Jun 2020} \vspace{-0.1cm}
\hspace{0.71cm} Collaboration research (Green Bank Observatory press release)  \\
\cvitemwithcomment{}{\hspace{0.4cm}${\color{color1} \circ}\;$ {\color{color1} \href{https://www.jpl.nasa.gov/news/news.php?feature=6998}{``\textit{Listening for Gravitational Waves Using Pulsars}''}}}{Nov 2017} \vspace{-0.1cm}
\hspace{0.71cm} Collaboration research (JPL press release)  \\
%\cvitemwithcomment{}{\hspace{0.4cm}${\color{color1} \circ}\;$ {\color{color1} \href{https://www.simonsfoundation.org/2017/11/13/gravitational-waves-supermassive-black-hole-merger/}{``\textit{Gravitational Waves from Merging Supermassive Black Holes}}}}{Nov 2017} \vspace{-0.1cm}
%\hspace{0.71cm} {\color{color1} \href{https://www.simonsfoundation.org/2017/11/13/gravitational-waves-supermassive-black-hole-merger/}{\textit{Will Be Spotted within 10 Years, New Study Predicts}''}} \\ \vspace{-0.1cm}
%\hspace{0.55 cm} Collaboration collaboration research (Simons Foundation press release) \vspace{0.1cm}\\
\cvitemwithcomment{}{\hspace{0.4cm}${\color{color1} \circ}\;$ {\color{color1} \href{https://public.nrao.edu/news/pressreleases/2016-nanograv-sbr}{``\textit{Gravitational Wave Search Provides Insights into Galaxy Evolution and Mergers}''}}}{Apr 2016} \vspace{-0.1cm}
\hspace{0.71cm} Collaboration research  (NRAO press release)
\end{comment}
\begin{comment}
\subsection{Media coverage}
\begin{itemize}[leftmargin=8mm]
\item Science Interview for National Geographic November 2009
        			\newline Interviewed for \emph{Phenomena: A science salon hosted by National Geographic}
		about the physics in the movie ``Men Who Stare at Goats''.


\item Research profiled in the popular-science book {\color{color1} \href{https://books.google.com/books/about/Ripples_in_Spacetime.html?id=YicuDwAAQBAJ&hl=en}{``Ripples in Spacetime: Einstein, Gravitational Waves, and the Future of Astronomy''}} by Govert Schilling (forward by Martin Rees), Harvard University Press (2017)
\item Interviewed and quoted by \textit{Science} magazine: {\color{color1} \href{http://science.sciencemag.org/content/351/6278/1124}{``In Search of Spacetime Megawaves''}} by Daniel Clery, Science  11 Mar 2016: Vol. 351, Issue 6278, pp. 1124-1125
\item Quoted, with research featured in {\color{color1} \href{https://www.syfy.com/syfywire/pulsars-black-holes-spacetime-center-of-the-solar-system}{\textit{SyFy}}} (article by Phil Plait), {\color{color1} \href{http://gizmodo.com/we-could-find-even-more-gravitational-waves-soon-with-p-1761021828}{\textit{Gizmodo}}}, {\color{color1} \href{https://www.engadget.com/2016/02/25/pulsars-gravitational-waves-black-holes/}{\textit{Engadget}}}, {\color{color1} \href{http://phys.org/news/2016-02-pulsar-web-low-frequency-gravitational.html}{\textit{Phys.org}}},  {\color{color1} \href{http://www.astronomy.com/news/2016/02/pulsar-web-could-detect-gravitational-waves}{\textit{Astronomy magazine}}}, {\color{color1} \href{http://www.universetoday.com/127562/the-future-of-gravitational-wave-astronomy-enhanced-ligo-pulsar-webs-space-interferometers-and-everything/}{\textit{Universe Today}}}
\item Collaboration research featured in {\color{color1} \href{https://www.sciencedaily.com/releases/2016/04/160405122609.htm}{\textit{Science Daily}}}, {\color{color1} \href{https://astronomynow.com/2016/04/06/gravitational-wave-search-provides-insights-into-galaxy-mergers/}{\textit{Astronomy Now} (online)}}
\end{itemize}
\end{comment}

%----------------------------------------------------------------------------------------
%  FULL PRESENTATIONS
%----------------------------------------------------------------------------------------
%\pagebreak
\section{Full Presentation List}
%\vspace{-0.3cm}
\subsection{Invited talks} %\vspace{-0.6cm}
\renewcommand\labelenumi{\bfseries\theenumi .}

\begin{etaremune}[leftmargin=8mm]
\small
\invtalkitem{Gravitational Wave Physics and Astronomy Workshop Plenary}{December, 2021}{Current Status of Pulsar Timing Array Gravitational Wave Astronomy}
\invtalkitem{University of South Carolina Colloquium}{December, 2021}{The Search for Lumbering Giants}
\invtalkitem{Idaho State University Colloquium}{October, 2021}{The Search for Lumbering Giants}
\invtalkitem{Gravitational Wave Astronomy Northwest}{July, 2021}{Pulsar Timing Array Gravitational Wave Astronomy Update}
\invtalkitem{Los Alamos National Lab}{April, 2021}{Searching for Nanohertz Gravitational Waves with a Galactic-Scale Detector}
\invtalkitem{University of Missouri}{March, 2021}{Searching for Nanohertz Gravitational Waves with a Galactic-Scale Detector}
\invtalkitem{Univ. of Wisc. Milwaukee, Center for Grav., Cosmo. and Astroph. Seminar}{February, 2021}{Doubling Down on Single Source Sensitivity}
\invtalkitem{CERN Theory Colloquium}{January, 2021}{Highlights from the Search for Gravitational Waves in NANOGrav Datasets}
\invtalkitem{Gravitational Wave Astronomy Northwest}{June, 2020}{Update on the search for gravitational waves in NANOGrav and IPTA datasets}
\invtalkitem{LIGO Hanford Seminar}{March, 2020}{The Search for Lumbering Giants}
\invtalkitem{American Astronomical Society 235th Meeting, NANOGrav Special Session}{January, 2020}{Highlights from the search for gravitational waves in NANOGrav datasets}
\invtalkitem{Montana State University, Physics Colloquium}{November, 2019}{Exploring the discovery space of pulsar timing arrays with realistic sensitivity curves}
\invtalkitem{Whitman College, Physics Colloquium}{October, 2019}{The Search for Lumbering Giants:\\ Observing the Nanohertz Gravitational-Wave Sky with Pulsar Timing Arrays}
\invtalkitem{22nd International Conference on General Relativity and Gravitation (GR22)\\ \& 13th Edoardo Amaldi Conference on Gravitational Waves (Amaldi13)}{July, 2019}{Education and Public Outreach Efforts by Pulsar Timing Array Collaborations}
\invtalkitem{Northwest APS Meeting}{May, 2019}{The Search for Lumbering Giants:\\Observing the Nanohertz Gravitational-Wave Sky with Pulsar Timing Arrays}
\invtalkitem{Gravitational Wave Physics and Astronomy Workshop}{December, 2019}{Current Status of Pulsar Timing Array Gravitational Wave Astronomy}
\invtalkitem{University of Washington Bothell Physical Sciences Division Seminar}{December, 2018}{Observing the Nanohertz Gravitational-Wave Sky with Pulsar Timing Arrays}
\invtalkitem{University of Washington Seattle AstroLunch Talk}{February, 2018}{A Galactic Scale Gravitational Wave Detector: The NANOGrav 11yr Limits}

\invtalkitem{University of Washington Bothell Physical Sciences Division Seminar Seminar}{November, 2017}{The NANOGrav Pulsar Timing Array:\\Using simulations to characterize our galactic gravitational wave detector.}
\invtalkitem{University of Texas Rio Grande Valley Arecibo Remote Command Center Meeting}{February, 2017}{Simulating Pulsar Signals for Noise Characterization of PTAs}
\invtalkitem{University of Arkansas Physics Colloquium}{February, 2016}{Gravitational Wave Astronomy in the 2nd Century of GR}
\invtalkitem{Western Washington University Physics Colloquium}{May, 2015}{A New Window into the Cosmos}
\invtalkitem{Brigham Young University Physics Theory Seminar}{February, 2015}{Gravitational Gauge Theory and the Dark Cosmological Constituents}
\invtalkitem{Georgia Tech Center for Relativistic Astrophysics, Departmental Colloquium}{March, 2013}{Biconformal Space \& Testing Alternative Theories of Gravity using Multi-Messenger Astronomy}
\invtalkitem{Utah State University Physics Colloquium}{February, 2013}{Best Practices for the Online Classroom}
\invtalkitem{Utah State University Physics Colloquium}{September 2010}{Curved Phase Space from conformal symmetry}
\invtalkitem{Oregon State Physics Colloquium}{March 2009}{Spherical Shells in a Schwarzschild Background}

\end{etaremune}
%\vspace{-0.6cm}
\subsection{Contributed presentations} %\vspace{-0.6cm}

\renewcommand\labelenumi{\bfseries\theenumi .}
\begin{etaremune}[leftmargin=8mm]
\small
\talkitem{Full PTA Advanced Noise Modeling Update}{NANOGrav Fall Meeting}{Virtual/Nashville TN, October, 2021}
\talkitem{Comparing Single-Source Statistics for PTA Observing Strategies}{American Physical Society April Meeting}{Virtual, April, 2021}
\talkitem{Doubling Down on Single Source Sensitivity}{American Astronomical Society Meeting}{Virtual, January, 2021}
\talkitem{Model Dependence of Bayesian Gravitational Wave Background Statistics in PTAs}{International Pulsar Timing Array Meeting}{Virtual, September, 2020}
\talkitem{Predicting NANOGrav's Sensitivity into the future with \texttt{hasasia}}{American Physical Society April Meeting}{Virtual, April, 2020}
\talkitem{Exploring the Nanohertz Gravitational-Wave Discovery Space with Sensitivity Curves and \texttt{hasasia}}{American Astronomical Society Meeting}{Honolulu, HI, January, 2020}
\talkitem{Gravitational Wave Astronomy with the NANOGrav Pulsar Timing Array}{Texas Symposium on Relativistic Astrophysics}{Portsmouth, UK, December, 2019}
\talkitem{Modeling Astrophysical Noise Sources in PTAs}{Fall NANOGrav Meeting}{Ithaca, NY, October, 2019}
\talkitem{Realistic Pulsar Timing Array Sensitivity Curves}{GR22/Amaldi13}{Valencia, Spain, July, 2019}
\talkitem{Pulsar Timing Array Sensitivity Curves}{American Physical Society April Meeting}{Denver, Colorado, April, 2019}
\talkitem{Characterizing the Sensitivity of the NANOGrav 11-year Data Set}{Spring NANOGrav Meeting} Bothell, Washington, March, 2019
\talkitem{Bayesian Monitoring of Solar Electron Density Using NANOGrav Data sets}{American Astronomical Society Meeting}{Seattle, Washington, January, 2019}
\talkitem{Bayesian Monitoring of the Solar Wind with Pulsar Timing Arrays}{AstroNWxSW}{Vancouver, British Columbia, November, 2018}
\talkitem{Spurious Gravitational Wave Detections in the NANOGrav 11 Year Data Set}{Fall NANOGrav Meeting}{Green Bank, West Virginia, October, 2018}
\talkitem{The International Pulsar Timing Array Mock Data Challenge}{LISA Symposium} Chicago, Illinois, July, 2018
\talkitem{Evolution of the Detection Statistics in the NANOGrav Dataset}{International Pulsar Timing Array Meeting}{Albuquerque, New Mexico, June, 2018}
\talkitem{Noise Evolution in the NANOGrav 11 Year Data Set}{Northwest Section APS Meeting}{Tacoma, Washington, June, 2018}
\talkitem{Publishing a Gravitational Wave Stochastic Background Analysis}{Python in Astronomy}{New York, New York, May, 2018}
\talkitem{Slicing the NANOGrav 11 Year Data Set}{American Physical Society April Meeting}{Columbus, Ohio, April, 2018}
\talkitem{Evolution of the NANOGrav 11 Year Data Set}{Spring NANOGrav Meeting}{Charlottesville, Virginia, March, 2018}
\talkitem{Slicing the NANOGrav 11 Year Data Set}{Fall NANOGrav Meeting} Easton, Pennsylvania, October, 2017
\talkitem{The NANOGrav pulsar signal simulator}{International Pulsar Timing Array}{S\`{e}vres, France, July, 2017}
\talkitem{Late-time quadrupolar gravitational wave power in de Sitter space}{American Physical Society April Meeting}{Washington, DC, January, 2017}
\talkitem{Null Stream Approach with PTAs: Noise Characterization and Excess Power}{American Astronomical Society 227th Meeting}{Grapevine, Texas, January, 2017}
\talkitem{Assessing the null stream approach for source localization in PTAs}{Fall NANOGrav Meeting}{Urbana, Illinois, October, 2016}
\talkitem{Comparing transverse-traceless decompositions of symmetric tensors}{Int. Soc. for General Relativity and Gravitation 21st Meeting}{New York City, New York, July, 2016}
\talkitem{Null Stream Approach for finding Sky Position of Pulsar Timing Array sources}{American Physical Society April Meeting}{Salt Lake City, Utah, April, 2016}
\talkitem{A Cartan Geometry approach to the AdS/CFT}{Midwest Gravity Meeting}{Evanston, Illinois, October, 2015}
\talkitem{Tracing the AdS/CFT Degrees of Freedom using Cartan Geometry}{American Physical Society April Meeting}{Baltimore, Maryland, April 2015}
\talkitem{Conformal gravity, dark matter and time}{Midwest Gravity Meeting}{Rochester, MI, November, 2014}
\talkitem{Conformal gravity, dark matter and time}{APS Four Corners Meeting}{Orem, Utah, October 2014}
\talkitem{Time from the conformal symmetries of a Euclidean space}{Midwest Gravity Meeting} Milwaukee, Wisconsin, October 2013
\talkitem{Lorentzian geometry from the conformal symmetries of a Euclidean space}{Loops 13: International Conference on Quantum Gravity}{Waterloo, Canada, July 2013}
\talkitem{Testing Bimetric and Massive Gravity Theories using Multi-Messenger Astronomy}{GR20/AMALDI$\;$10}{Warsaw, Poland, July 2013}
\talkitem{Lorentzian spin connection from the conformal symmetries of a Euclidean space}{53rd Cracow School of Theoretical Physics}{Zakopane, Poland, June 2013}
\talkitem{General relativity in signature changing phase space}{Pacific Coast Gravity Meeting}{Davis, California, March 2013}
\talkitem{General relativity in phase space with a natural notion of time}{Pacific Coast Gravity Meeting}{Santa Barbara, California, March 2012}
\talkitem{A systematic construction of curved phase space: A gravitational gauge theory with symplectic form}{Loops 11: International Conference on Quantum Gravity}{Madrid, Spain, May 2011}
\talkitem{Quantum gravity in relativistic phase space}{Intermountain Graduate Research Symposium}{Logan, Utah, March 2010}
\talkitem{Multiple Spherical Shells in Schwarzschild Spacetime}{12th Marcel Grossman Gravity Meeting}{Paris, France, July 2009}
\talkitem{Single Spherical Shells in Schwarzschild Spacetime}{Pacific Coast Gravity Meeting}{Eugene, Oregon, March 2009}


\end{etaremune}
%\vspace{-0.6cm}
\subsection{Posters}
\begin{etaremune}[leftmargin=8mm]
\small
\talkitem{The NANOGrav Pulsar Signal Simulator}{American Astronomical Society Meeting}{Honolulu, HI, January, 2020}
\talkitem{Pulsar Timing Array Source Location Using the Null Signal Approach}{American Astronomical Society 225th Meeting}{Seattle, Washington, January 2015}
\talkitem{Multiple Spherical Shells in Schwarzschild Spacetime}{TEXAS Symposium on Relativistic Astrophysics}{Vancouver, Canada, December 2008}
\end{etaremune}

\begin{comment}
\newpage
\section{References}


	\renewcommand\labelitemi{\blucirc}
	\begin{itemize}[leftmargin=8mm]
	\setlength\itemsep{0.05mm}
	\item \textbf{Dr. Xavier Siemens} \emph{NANOGrav PI/ Collaborator}
        		\newline Professor of Physics
		\newline Oregon State University, Corvallis, OR 97331
		\newline \emph{Phone:} 541-737-7512 \qquad \emph{email:} \url{xavier.siemens@oregonstate.edu}
		\newline
	\item \textbf{Dr. Stephen Taylor} \emph{NANOGrav Detection Working Group Co-chair/ Collaborator}
       		\newline Professor of Physics
		\newline Vanderbilt University, Nashville, TN 37235
		\newline \emph{Phone:} 615-322-7311 \qquad email:\url{stephen.r.taylor@vanderbilt.edu}
		\newline
	\item \textbf{Dr. Joey Key} \emph{Post Doctoral Advisor}
       		\newline Professor of Physics
		\newline University of Washington Bothell, Bothell, WA 98011
		\newline \emph{Phone:} 425-352-5497 \qquad email:\url{joeykey@uw.edu}
		\newline
	\item \textbf{Dr. Joseph Romano} %\emph{Post Doctoral Advisor}
       		\newline Professor of Physics
		\newline Texas Tech University, Lubbock, TX 79409
		\newline \emph{Phone:} 806-834-6522 \qquad email:\url{joseph.d.romano@ttu.edu}
		\newline
	\item \textbf{Dr. James T. Wheeler} \emph{PhD Advisor, Utah State University}
        		\newline Associate Professor of Physics
		\newline Utah State University, Logan, UT 84321
		\newline \emph{Phone:} 435-770-7601 \qquad email:\url{jim.wheeler@usu.edu}
		\newline
	\item \textbf{Dr. Tevian Dray} \emph{MS Advisor, Oregon State University}
     		\newline Professor of Mathematics
		\newline Oregon State University, Corvallis, OR 97331
		\newline \emph{Phone:} 	541-737-5159 \qquad \emph{email:} \url{tevian@math.oregonstate.edu}
		\newline
	\item \textbf{Dr. Jan Sojka}
        		\newline Department Chair \& Professor of Physics
		\newline Utah State University, Logan, UT 84321
		\newline \emph{Phone:} 435-797-2857 \qquad email: \url{jan.sojka@usu.edu}
		\newline

	\item \textbf{Dr. Damon T. Spayde} %\emph{Teaching Reference}
       		\newline Department Chair \& Associate Professor of Physics
		\newline Hendrix College, Conway, AR 72032
		\newline \emph{Phone:} 501-450-1251 \qquad email:\url{spayde@hendrix.edu}
		\newline
	\item \textbf{Dr. Shane Larson} \emph{Collaborator}
        		\newline Research Associate Professor
		\newline Center for Interdisciplinary Exploration and Research in Astrophysics (CIERA)
		\newline Northwestern University, Evanston, IL 60208
		\newline \emph{Phone:} 847-467-4305 \qquad \emph{email:}\url{s.larson@northwestern.edu}
		\newline
	\item \textbf{Dr. Todd Tinsley} %\emph{Teaching Reference}
       		\newline Associate Professor of Physics
		\newline Hendrix College, Conway, AR 72032
		\newline \emph{Phone:} 501-450-1404 \qquad email:\url{tinsley@hendrix.edu}
		\newline

	\end{itemize}
%\subsection{Teaching}
\end{comment}

\end{document}
