\pubitem{{Heliosphere Meets Interstellar Medium, in a Galactic Context}}
         {Stella Koch~{Ocker}, [...], \textbf{J.~S.~{Hazboun}}, et al. [11 Authors]}
         {https://arxiv.org/abs/2208.11804}
         {{Arxiv:}2208.11804}

\pubitem{{Pulsar Timing Arrays: Gravitational Waves from Supermassive Black Holes and More}}
         {I.~{Stairs}, [...], \textbf{J.~S.~{Hazboun}}, et al. [32 Authors]}
         {https://doi.org/10.5281/zenodo.3756164}
         {{Canadian Long Range Plan for Astronony and Astrophysics White Papers}, \textbf{2020}, pp. 16, (2019)}

\pubitem{{The NANOGrav Program for Gravitational Waves and Fundamental Physics}}
         {S.~{Ransom}, [...], \textbf{J.~S.~{Hazboun}}, et al. [15 Authors]}
         {https://arxiv.org/abs/1908.05356}
         {{Bulletin of American Astronomical Society}, \textbf{51}, pp. 195, (2019)}

\pubitem{{NANOGrav Education and Outreach: Growing a Diverse and Inclusive Collaboration for Low-Frequency Gravitational Wave Astronomy}}
         {Timothy~{Dolch}, [...], \textbf{J.~S.~{Hazboun}}, et al. [27 Authors]}
         {https://arxiv.org/abs/1907.07348}
         {{Bulletin of American Astronomical Society}, \textbf{51}, pp. 254, (2019)}

\pubitem{{The Gravitational View of Massive Black Hole Mergers}}
         {Monica~{Colpi}, [...], \textbf{J.~S.~{Hazboun}}, et al. [19 Authors]}
         {https://arxiv.org/abs/1903.06867}
         {{Bulletin of American Astronomical Society}, \textbf{51}, 3, (2019)}

\pubitem{{Physics Beyond the Standard Model With Pulsar Timing Arrays}}
         {Xavier~{Siemens}, \textbf{J.~S.~{Hazboun}}, et al. [8 Authors]}
         {https://arxiv.org/abs/1907.04960}
         {{Bulletin of American Astronomical Society}, \textbf{51}, 3, (2019)}

\pubitem{{The Second International Pulsar Timing Array Mock Data Challenge}}
         {\textbf{J.~S.~Hazboun}, C.~ M.~F.~{Mingarelli}, K.~J.~{Lee}}
         {https://arxiv.org/abs/1810.10527}
         {{Arxiv:}1810.10527}

\pubitem{{Null-stream pointing with pulsar timing arrays}}
         {\textbf{J.~S.~Hazboun}, S.~L.~{Larson}}
         {https://arxiv.org/abs/1607.03459}
         {{Arxiv:}1607.03459}

\pubitem{{Limiting alternative theories of gravity using gravitational wave observations across the spectrum}}
         {\textbf{J.~S.~Hazboun}, M.~P.~{Marcano}, S.~L.~{Larson}}
         {https://arxiv.org/abs/1311.3153}
         {{Arxiv:}1311.3153}

